Spike spectra for recurrences

### 2022-07-20 Manuscript/inter_spike_manuscript_mdpi.tex
Switched format for entropy journal (MDPI)

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
\documentclass[smallcondensed]{svjour3}    % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{siunitx}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
%
% Insert the name of "your journal" with
\journalname{Nonlinear Dynamics}
%
\begin{document}

\title{Recurrence spike spectra}

\titlerunning{Recurrence spike spectra}        % if too long for running head

\author{K. Hauke Kraemer \and
		Frank Hellmann \and
		Mehrnaz Anvari \and
        J\"urgen Kurths \and 
        Norbert Marwan
}

\institute{K. Hauke Kraemer \and J\"urgen Kurths \and Norbert Marwan \and Frank Hellmann \and Mehrnaz Anvari \at Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, 
Germany \email{hkraemer@pik-potsdam.de}\and
           K. Hauke Kraemer \and J\"urgen Kurths \at Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany \and
		   Norbert Marwan \at Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany \and
		   J\"urgen Kurths \at Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
We invent this instructive approach with the 
idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.

\keywords{Bifurcations \and Recurrence Analysis \and Decomposition \and Frequency Analysis}
\PACS{05.45.Tp, 05.90.+m, 89.90.+n, 02.70.Uu, 05.10.Ln, 05.45.-a, 05.45.Ac}
\end{abstract}

@@

In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter spike spectrum} does not show resonance 
behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
FT. In Section \ref{sec_tau_rr_application} we exemplify \sout{its use} \todo{the usage of inter spike spectrum} when transforming the $\tau$-RR of a system under study. In this case, the inter spike spectrum can unravel 
characteristic time scales of high dimensional systems, which is not possible when using a FT. \todo{Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized}

\section{Method}\label{sec_tau_rr_method}

The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal \todo{what do you mean with any signal? do you mean to look at data set instead of $\tau$-RP or RP?}-- 
is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal \todo{which} we want to transform. \sout{with}\todo{The signal has} length $N$ and 
$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
vector $\bf{s}$. 
First, $\tilde{N}$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
for possible phase shifts of 
these basis functions occurring in $\bf{s}$, each of these $\tilde{N}$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
$M = \sum_{i=1}^{\tilde{N}}i$ 
basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure) \todo{$T$ in the following eqs. should not be $T_{is}$ to be consistent with the text?}\todo{$n$ in eq.6 is not clear for me}
\begin{align}
\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT(i)-i+T(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
T(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
\label{eq_basis_matrix}
\end{align}
Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter spike period, 
if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, here 
the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
Fig.~\ref{fig_tau_rr_basis_functions}B).\\

\noindent Eventually, an under-determined linear system
\begin{equation}
\bf{X}^T\bf{\beta}=\bf{s}
\label{eq_linear_system}
\end{equation}  
has to be solved for $\bf{\beta}$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
particularly interested in those solutions, which promote sparsity in $\bf{\beta}$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\bf{\beta}}$. Finally, we group loadings 
which correspond to basis functions having the same period 
$T_\text{is}$ into $\hat{\bf{\beta}}_f$ and obtain the 
\textit{inter spike spectrum} by simply plotting $\hat{\bf{\beta}}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
(Fig.~\ref{fig_tau_rr_dirac_comb}C, F).

@@

In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the proposed method \todo{which method? STLS?}must also deal with the free choice of the regression regularization parameter $\alpha$, 
which determines the sparsity of the regression coefficient vector $\hat{\bf{\beta}}$. Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small, 
since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\bf{\beta}}$ is an exact solution of Eq.~\ref{eq_linear_system} and not sparse. On the other hand, only a sparse number 
of non-zero loadings in $\hat{\bf{\beta}}$ -- \textit{aka} \todo{what is aka?}peaks in the inter spike spectrum -- are obtained when $\alpha$ is sufficiently large. In this paper we select $\alpha$ such that the 
re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\bf{\beta}}$ matches a given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.

\section{Application}\label{sec_tau_rr_application}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler}
 \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
 \textbf{A} Trajectory of the system in a period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
 \textbf{C} in a chaotic regime (parameter $a=0.428$). 
 \textbf{D, E, F} The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for D \& E and 5\% for F. 
  \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a LASSO regression and a regularization threshold 
  corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
\todo[inline]{why you have not used STLS method here?} }
\label{fig_tau_rr_example_roessler}
\end{figure}

@@

\section{Conclusion}\label{sec_tau_rr_conclusion}

@@

\begin{acknowledgements}
This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9). All computations have been carried out in MATLAB\textsuperscript{\textregistered} 
and the Julia language and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
\section*{Conflict of interest}

The authors declare that they have no conflict of interest.

\section*{Code availability}

The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language **Package will be published and cited here, 
when accepted** and as a MATLAB\textsuperscript{\textregistered} toolbox 
**Toolbox will be published and cited here, when accepted**.

\clearpage
\appendix
\section{Inter spike spectra for noisy R\"ossler system}

>>>>

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[entropy,article,submit,pdftex,moreauthors]{Definitions/mdpi} 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal and change "submit" to "accept". The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, alloys, analytica, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, currophthalmol, cyber, dairy, data, dentistry, dermato, dermatopathology, designs, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, ent, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, futureinternet, futureparasites, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, hazardousmatters, healthcare, hearts, hemato, heritage, highthroughput, histories, horticulturae, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijtm, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jzbg, kidney, kidneydial, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing, nanomaterials, ncrna, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology, pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, sports, standards, stats, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
% MDPI internal commands
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2022}
\copyrightyear{2022}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{} 
%\daterevised{} % Only for the journal Acoustics
\dateaccepted{} 
\datepublished{} 
%\datecorrected{} % Corrected papers include a "Corrected: XXX" date in the original paper.
%\dateretracted{} % Corrected papers include a "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, cleveref, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\newcommand\hmmax{0}
\newcommand\bmmax{0}

\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{mathptmx}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{siunitx}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Spike spectra for recurrences}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Spike spectra for recurrences}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-9943-5391} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{K. Hauke Kraemer $^{1,}$*\orcidA{}, Frank Hellmann $^{1,}$, Mehrnaz Anvari $^{1,4}$, J\"urgen Kurths $^{1,2,4}$ and Norbert Marwan $^{1,3,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{K. Hauke Kraemer, Frank Hellmann, Mehrnaz Anvari, J\"urgen Kurths and Norbert Marwan}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Kraemer, K.H..; Hellmann, F.; Anvari M.; Kurths, J.; Marwan, N.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Potsdam Institute for Climate Impact Research, Member of the Leibniz Association, 14473 Potsdam, Germany\\
$^{2}$ \quad Institute of Physics and Astronomy, University of Potsdam, 14476 Potsdam, Germany\\
$^{3}$ \quad Institute of Geosciences, University of Potsdam, 14476 Potsdam, Germany\\
$^{4}$ \quad Institute of Physics, Humboldt Universit\"at zu Berlin, 12489 Berlin, Germany}

% Contact information of the corresponding author
\corres{Correspondence: hkraemer@pik-potsdam.de; marwan@pik-potsdam.de}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A novel kind of power spectrum is constructed, the \textit{inter spike spectrum}, which transforms any signal into its spike-frequency domain. This method 
clearly shows the apparent cycles in the data and overcomes the problems for spike-train-like signals when using the obvious idea of Fourier-transforming it. 
We invent this instructive approach with the 
idea of transforming the $\tau$-recurrence rate of a recurrence plot (RP), which often has a spiky appearance. The $\tau$-recurrence rate is the density of recurrence points 
along diagonals of the RP, which are parallel to the main diagonal with a distance of $\tau$. In this context the inter spike spectrum can be interpreted as a nonlinear power 
spectrum of a potentially high dimensional system which constitutes the RP. The proposed measure is robust to noise and is able to detect and analyze bifurcations.}

% Keywords
\keyword{Decomposition; Frequency Analysis; Recurrence Analysis; Bifurcations}
\PACS{05.45.Tp, 05.90.+m, 89.90.+n, 02.70.Uu, 05.10.Ln, 05.45.-a, 05.45.Ac}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

In this article we propose a new way of transforming a spike-train-like signal into its frequency domain. This novel \textit{inter spike spectrum} does not show resonance 
behavior of the signal's inherent inter-spike frequencies (Fig.~\ref{fig_tau_rr_dirac_comb}C, F). Section \ref{sec_tau_rr_method} explains the idea, which can be used to decompose 
any arbitrary signal and is not restricted to the $\tau$-RR, which we exemplify here. However, the more spiky the signal is, the more outstanding our new approach is compared to a 
FT. In Section \ref{sec_tau_rr_application} we exemplify the usage of inter spike spectrum when transforming the $\tau$-RR of a system under study. In this case, the inter spike spectrum 
can unravel characteristic time scales of high dimensional systems, which is not possible when using a FT. Finally, in Section \ref{sec_tau_rr_conclusion} our results are summarized.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Method}\label{sec_tau_rr_method}

The signal, which we would like to transform -- we focus on $\tau$-RR in this article, but this can be applied to any sort of signal \todo{MA: what do you mean with any signal? do you mean to look at data set instead of $\tau$-RP or RP?}-- 
is decomposed into a set of appropriate basis functions. Instead of using trigonometric functions, as it is the idea in the Fourier decomposition, we use Dirac combs (DC) with 
different inter-spike periods as basis functions, Eq.~\eqref{eq_dirac_comb}. Let $s(t_i)$ be the normalized signal we want to transform of length $N$ and 
$t_i=i\cdot \Delta t,~i=1,\ldots,N$, where $\Delta t$ denotes the sampling time and $s(t_i) \in [0,\ 1]\ \forall\ i$. In the following we label this time series as a $(1\times N)$-dimensional 
vector $\bf{s}$. 
First, $\tilde{N}$ different DC's of length $N$ are constructed with inter-spike periods $T_\text{is} \in [1,\ldots,\tilde{N}]$ and $\tilde{N}=\ceil*{N/2}+1$. Second, in order to account 
for possible phase shifts of 
these basis functions occurring in $\bf{s}$, each of these $\tilde{N}$ different DC's also need to be shifted one step further $T_\text{is}-1$ times. This leaves us with a total number of 
$M = \sum_{i=1}^{\tilde{N}}i$ 
basis functions which we can arrange as rows of a $(M\times N)$-sized matrix $\bfX$
(Fig.~\ref{fig_tau_rr_basis_functions}A illustrates the described procedure) \todo{MA: $n$ in eq.6 is not clear for me}
\begin{align}
\bfX_{i,j} &= \sum_{k=0}^{N}\delta\left(j-1-kT_\text{is}(i)-i+T_\text{is}(i) \right), \quad i=1,\dots,\ceil*{N/2}+1, \quad j=1,\dots,N\\
T_\text{is}(i)&= n \quad, \forall n:~ \frac{n(n-1)}{2} + 1 \leq i <  \frac{n(n+1)}{2} + 1,\quad n \in \mathbb{N}_+.
\label{eq_basis_matrix}
\end{align}
Note that due to the shifting of each of the basis functions of inter-spike period $T_\text{is}$, $\bfX$ is not linear independent anymore. 
Furthermore, there will be identical basis functions and also basis functions, which do not allow for an unambiguous inter spike period, 
if we would include all $N$ possible inter spike periods for a signal of length $N$ instead of $\ceil*{N/2}+1$ (Fig.~\ref{fig_tau_rr_basis_functions}A). 
The reason is that in contrast to a trigonometric decomposition, where the Nyquist frequency marks a lower bound for the corresponding wave period, here 
the maximum considered inter spike period is bounded by $T_{\text{is}}^{\text{max}} = \ceil*{N/2}+1$ (schematically illustrated in 
Fig.~\ref{fig_tau_rr_basis_functions}B).\\

\noindent Eventually, an under-determined linear system
\begin{equation}
\bf{X}^T \boldsymbol\beta=\bf{s}
\label{eq_linear_system}
\end{equation}  
has to be solved for $\boldsymbol\beta$, a $(M\times 1)$-sized vector carrying the loadings we are interested in. Along a variety of algorithms which can solve this problem, we are 
particularly interested in those solutions, which promote sparsity in $\boldsymbol\beta$, since our goal is to decompose the signal $\bfs$ into a minimal number of basis 
functions (for an excellent overview of the topic we refer to \citet{Brunton2019}). In this paper we either use the \textit{least absolute shrinkage and selection operator} 
(LASSO) \cite{Tibshirani1996} or a \textit{sequentially thresholded least squares} (STLS) regression \cite{Brunton2016,Brunton2019} to obtain a solution $\hat{\boldsymbol\beta}$. Finally, we group loadings 
which correspond to basis functions having the same period 
$T_\text{is}$ into $\hat{\boldsymbol\beta}_f$ and obtain the 
\textit{inter spike spectrum} by simply plotting $\hat{\boldsymbol\beta}_f$ as a function of the frequency $f=T_\text{is}^{-1}$, with $T_\text{is}=\Delta t, 2\Delta t, \dots, (\ceil*{N/2}+1) \Delta t$ 
(Fig.~\ref{fig_tau_rr_dirac_comb}C, F).

@@

In addition to the computational complexity of solving Eq.~\eqref{eq_linear_system}, the solving algorithm must also deal with the free choice of the regression regularization parameter $\alpha$, 
which determines the sparsity of the regression coefficient vector $\hat{\boldsymbol\beta}$. Obviously, there will be numerous peaks in the inter spike spectrum of a given signal, when $\alpha$ is small, 
since $\alpha=0$ corresponds to the least squares solution and the corresponding $\hat{\boldsymbol\beta}$ is an exact solution of Eq.~\ref{eq_linear_system} and not sparse. On the other hand, 
only a sparse number of non-zero loadings in $\hat{\boldsymbol\beta}$, i.e., peaks in the inter spike spectrum, are obtained when $\alpha$ is sufficiently large. 
The actual implementation of the regularization depends on the regression method chosen (in our case, LASSO or STLS), and consequently a given value of $\alpha$ will generally result in 
different sparse loading vectors $\hat{\boldsymbol\beta}$. Therefore, in this paper we select $\alpha$ such that the re-composed signal $\tilde{\bf{s}}=\bf{X}^T\hat{\boldsymbol\beta}$ matches a 
given (Pearson) correlation coefficient $\rho$ between the original signal $\bf{s}$ and itself.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}\label{sec_tau_rr_application}

@@

\begin{figure}
 \centering
 \includegraphics[width=0.9\textwidth]{./figures/fig_tau_rr_example_roessler}
 \caption{Inter spike spectra of the $\tau$-RR of the R\"ossler system in three different dynamical regimes with parameters $b=2$, $c=4$. 
 \textbf{A} Trajectory of the system in a period-2 (parameter $a=0.36$), \textbf{B} in a period-3 (parameter $a=0.41$) and 
 \textbf{C} in a chaotic regime (parameter $a=0.428$). 
 \textbf{D, E, F} The corresponding RPs, obtained by using a recurrence threshold corresponding to a 10\% global 
 recurrence rate for D \& E and 5\% for F. 
  \textbf{G, H, I} $\tau$-RR's of the shown RPs. 
  \textbf{J, K, L} The proposed inter spike spectra of the $\tau$-RR's shown in panels G, H, I. Spectra were obtained with a LASSO regression and a regularization threshold 
  corresponding to $\rho=0.95$ accordance of $\tau$-RR's and re-composed signals. The distance ratio of the peaks reflect the limit cycle dynamic.  
  \textbf{M, N, P} Fourier power spectra of the $\tau$-RR's shown in panels G, H, I.
\todo[inline]{MA: why you have not used STLS method here?} }
\label{fig_tau_rr_example_roessler}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}\label{sec_tau_rr_conclusion}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, KHK and FH; methodology, KHK, FH and NM; software, KHK and FH; validation, KHK, FH, MA and NM.; formal analysis, KHK; data curation, KHK and MA; writing---original draft preparation, KHK; writing---review and editing, KHK, FH, MA and NM; visualization, KHK; supervision, NM; project administration, JK; All authors have read and agreed to the published version of the manuscript.}

\funding{This work has been financially supported by the German Research Foundation (DFG projects MA4759/8 and MA4759/9).}

\dataavailability{The study that we present here is available as a fully reproducible code base
**Repository will be published and cited here, when accepted** and the method
will be available in the Julia language **Package will be published and cited here, 
when accepted** and as a MATLAB\textsuperscript{\textregistered} toolbox 
**Toolbox will be published and cited here, when accepted**.}

\acknowledgments{
All computations have been carried out in MATLAB\textsuperscript{\textregistered} and the Julia language 
and made use of the packages \textit{DynamicalSystems.jl} \cite{datseris2018} and \textit{DifferentialEquations.jl} \cite{rackauckas2017}.
}

\conflictsofinterest{The authors declare that they have no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{yes} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix

\section{Inter spike spectra for noisy R\"ossler system}
